### 2018-04-12 linearity-2018/introduction.tex
First full draft.

We introduce the idea above of having a modality for exchange, but
what about a individual modalities for weakening and contraction?
Indeed it is possible to give modalities for these structural rules as
well using adjoint models.  Now that we have each structural rule
isolated into their own modality is it possible to put them together
to form new modalities that combine structural rules?  The answer to
this question has already been show to be positive, at least for
weakening and contraction, but we extend this line of work to include
exchange, and in the future associativity as well.
Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
adjunctions to accomplish the same, but in a more intuitive and
natural way.  Thus, this part of our work is a natural extension of
Melli{\'e}s'.

>>>>

%% We introduce the idea above of having a modality for exchange, but
%% what about a individual modalities for weakening and contraction?
%% Indeed it is possible to give modalities for these structural rules as
%% well using adjoint models.  Now that we have each structural rule
%% isolated into their own modality is it possible to put them together
%% to form new modalities that combine structural rules?  The answer to
%% this question has already been show to be positive, at least for
%% weakening and contraction, but we extend this line of work to include
%% exchange, and in the future associativity as well.
%% Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
%% modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
%% adjunctions to accomplish the same, but in a more intuitive and
%% natural way.  Thus, this part of our work is a natural extension of
%% Melli{\'e}s'.
